---
title: "Preprocessing APA PsycTests"
---

https://www.apa.org/pubs/databases/psyctests/field-guide

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(groundhog)
groundhog.library(c("tidyverse", "codebook", "xml2", "kableExtra", "tools", "stringi"), date = "2024-02-14")
source("0_functions.R")

```

## import records_wide
```{r}
load(file = "../sober_rubric/raw_data/records_wide.rda")
```


## Complexity of columns

I wrote a little summary function to find columns which always consist only of a length 1 list with a single element. These can be losslessly translated to simple vectors.

```{r}
col_structures <- records_wide %>% 
  ungroup() %>% 
  head(1000) %>% # looked only at 1000 to save time
  rowwise() %>% # row wise is necessary to determine the length of the list in each row
  mutate_all(~ 
               if_else(length(.) == 1, 
                       pluck_depth(.[[1]]),
                       pluck_depth(.))) %>% 
  ungroup() %>% 
  summarise_all(max) # take the maximum

# fetch all "simple" columns
col_structures %>% pivot_longer(everything()) %>%
  filter(value == 1) %>% pull(name) %>% 
  cat(sep = "\n")
# fetch all non-simple columns
col_structures %>% pivot_longer(everything()) %>% filter(value > 1) %>% pull(name) %>% cat(sep = "\n")
```


### hoist variables which are just length 1 lists to turn them into regular characters

Simplify all the simple list columns to character columns.

```{r}
records_wide <- records_wide %>% 
  hoist(DOI, DOI = list(1, 1), .remove = FALSE) %>%
  hoist(Name, Name = list(1, 1), .remove = FALSE) %>%
  hoist(Purpose, Purpose = list(1, 1), .remove = FALSE) %>%
  hoist(Description, Description = list(1, 1), .remove = FALSE) %>%
  hoist(InstrumentType, InstrumentType = list(1, 1), .remove = FALSE) %>%
  hoist(Format, Format = list(1, 1), .remove = FALSE) %>%
  hoist(SupportingDocumentationLink, SupportingDocumentationLink = list(1, 1), .remove = FALSE) %>%
  hoist(Commercial, Commercial = list(1, 1), .remove = FALSE) %>%
  hoist(Permissions, Permissions = list(1, 1), .remove = FALSE) %>%
  hoist(Fee, Fee = list(1, 1), .remove = FALSE) %>%
  hoist(TestYear, TestYear = list(1, 1), .remove = FALSE) %>%
  hoist(TestItemsAvailable, TestItemsAvailable = list(1, 1), .remove = FALSE) %>%
  hoist(Reliability, Reliability = list(1, 1), .remove = FALSE) %>%
  hoist(Validity, Validity = list(1, 1), .remove = FALSE) %>%
  hoist(FactorAnalysis, FactorAnalysis = list(1, 1), .remove = FALSE) %>%
  hoist(NumberOfTestItems, NumberOfTestItems = list(1, 1), .remove = FALSE) %>%
  hoist(TestReleaseDate, TestReleaseDate = list(1, 1), .remove = FALSE) %>%
  hoist(TestCorrectionDate, TestCorrectionDate = list(1, 1), .remove = FALSE) %>%
  hoist(FactorsAndSubscales, FactorsAndSubscales = list(1, 1), .remove = FALSE)

records_wide$Reliability <- str_replace_all(records_wide$Reliability, "[[:space:]]+", " ")
records_wide$Validity <- str_replace_all(records_wide$Validity, "[[:space:]]+", " ")
records_wide$FactorAnalysis <- str_replace_all(records_wide$FactorAnalysis, "[[:space:]]+", " ")
records_wide$FactorsAndSubscales <- str_replace_all(records_wide$FactorsAndSubscales, "[[:space:]]+", " ")

instrument_types <- tibble(InstrumentType = 
                             c("Inventory/Questionnaire", "Rating Scale", "Test", "Battery", 
                               "Index/Indicator", "Survey", "Screener", "Task", "Checklist", 
                               "Interview Schedule/Guide", "Diary", "Coding Scheme", "Projective Measure", 
                               "Q Sort", "Vignette/Scenario"),
                           instrument_type_broad = c("questionnaire", "questionnaire", "test", "test",
                                                     "questionnaire", "questionnaire", "questionnaire", "task", "other-rating",
                                                     "other-rating", "questionnaire", "other-rating", "task",
                                                     "questionnaire", "questionnaire"))
records_wide <- records_wide %>% left_join(instrument_types, by = "InstrumentType")

records_wide <- records_wide %>% 
  rowwise() %>% 
  mutate(classifications_n = length(ClassificationList)) %>% 
  ungroup() %>% 
  hoist(ClassificationList, classification_1 = list(1,1,1), .remove = FALSE) %>% 
  hoist(ClassificationList, classification_2 = list(2,1,1), .remove = FALSE) %>% 
  mutate(classification_1 = str_replace_all(classification_1, "[:space:]+", " "),
         classification_2 = str_replace_all(classification_2, "[:space:]+", " "))


records_wide <- records_wide %>% 
  mutate(TestYear = as.numeric(TestYear))
```


Set binary fields for "commercial" and "open".

```{r}
records_wide <- records_wide %>% 
  mutate(commercial_bin = case_when(
    Commercial == "Yes" ~ 1L,
    Commercial == "No" ~ 0L,
    Commercial == "Unknown" ~ NA_integer_
  ),
  open_bin = case_when(
    Permissions == "May use for Research/Teaching" ~ 1L,
    Permissions == "Not Specified" ~  NA_integer_,
    TRUE ~ 0L
  ))
```

## Extract first acronym
```{r}
records_wide <- records_wide %>% 
  hoist(AcronymList, first_acronym = list(1, 1), .remove = FALSE)

records_wide <- records_wide %>% 
  hoist(ConstructList, first_construct = list(1,1,1), .remove = FALSE)

table(records_wide$first_construct) %>% sort() %>% tail(20)

acronym_base <- str_replace(records_wide$first_acronym, "-R$", "")
length(unique(acronym_base))

acronym_base <- str_replace(acronym_base, "--.+$", "")
length(unique(acronym_base))

acronym_base <- str_replace(records_wide$first_acronym, "--.+$", "")
length(unique(acronym_base))

records_wide$acronym_base <- acronym_base

```


## Extract source citation DOI

Extract the source citation DOI. I didn't actually run this yet, want to do it with scopus where I can get citations by year.

```{r}
# records_wide <- records_wide %>% 
#   hoist(SourceCitationList, first_source_doi = list(1, "DOI", 1), .remove = FALSE)
# 
# source_dois <- records_wide %>% select(first_source_doi) %>% drop_na() %>% distinct()
# 
# # commented out for now
# # source_dois <- rcrossref::cr_citation_count(source_dois$first_source_doi)
# # records_wide <- records_wide %>% left_join(source_dois %>% rename(first_source_doi = doi, citation_count_crossref = count), by = "first_source_doi")
# 
# 
# library(rscopus)
# scopus_api_key <- "7804cba4fc15e860f8c5f549ac2215eb"
# find_cit_scopus <- function(x){
# 
# }
# for (i in seq_along(nrow(source_dois))) {
#   find_cit_scopus(source_dois$first_source_doi[i])
#   if(i %% 10 == 0) print(i, source_dois$first_source_doi[i])
# }
# existing <- readr::read_tsv("../sober_rubric/raw_data/scopus_citation_counts.tsv")
# for (i in seq_along(setdiff(source_dois$first_source_doi, existing$doi))) {
#   x <- source_dois$first_source_doi[i]
#   if(! x %in% existing$doi) {
#     s <- generic_elsevier_api(api_key = scopus_api_key,
#                               doi = x,
#                               date = "1980-2023",
#                               type = "citations",
#                               search_type = "scopus")
#     citations <- s$content$`abstract-citations-response`$citeColumnTotalXML$citeCountHeader$columnTotal %>% as.data.frame()
#     if(length(citations)) {
#       colnames(citations) <- s$content$`abstract-citations-response`$citeColumnTotalXML$citeCountHeader$columnHeading %>% as.data.frame()
#       citations <- pivot_longer(citations, everything(), names_to = "year", values_to = "citation_count", values_transform = as.numeric, names_transform = as.numeric)
#       citations$doi <- x
#     } else {
#       citations <- tibble(doi = x)
#     }
#     existing <- bind_rows(existing, citations)
#     readr::write_tsv(existing, "../sober_rubric/raw_data/scopus_citation_counts.tsv")
#   }
#   if(i %% 10 == 0) { cat(paste(i, source_dois$first_source_doi[i])) }
# }
# 
# 
# records_wide <- records_wide %>% distinct() %>% left_join(existing %>% group_by(doi) %>% summarise(citation_count = sum(citation_count, na.rm = T)), by = c("first_source_doi" = "doi"))
```


## Extract Cronbach's Alpha

```{r}
records_wide <- records_wide %>% 
  mutate(
    no_reliability = Reliability == "No reliability indicated.",
         first_reliability_match = as.numeric(str_match(Reliability, "(\\.\\d+)")[,2]),
         all_reliabilities = lapply(str_extract_all(Reliability, "(\\.\\d+)"), as.numeric)
)
```

## Prevalences of validity information

```{r}
table(records_wide$FactorAnalysis) %>% sort() %>% tail(2)
records_wide %>% group_by(InstrumentType) %>% 
  summarise(Reliability = mean(Reliability!="No reliability indicated."),
            FactorAnalysis = mean(FactorAnalysis!="No factor analysis indicated." & FactorAnalysis != "This is a unidimensional measure."),
            Validity = mean(Validity!="No validity indicated.")) %>%
  arrange(Reliability+FactorAnalysis+Validity) %>% 
  mutate(across(c(Reliability, FactorAnalysis, Validity), ~ round(100 * .)))

# records_wide %>% group_by(classification_1) %>% 
#   summarise(Reliability = mean(Reliability!="No reliability indicated."),
#             FactorAnalysis = mean(FactorAnalysis!="No factor analysis indicated." & FactorAnalysis != "This is a unidimensional measure."),
#             Validity = mean(Validity!="No validity indicated.")) %>% arrange(Reliability+FactorAnalysis+Validity) %>% View
```

## Sample size

```{r}
samplesizes <- records_wide$Reliability %>% str_match_all(regex("\\bn ?= ?(\\d+)", ignore_case = TRUE)) %>% map(~ as.numeric(.[,2]))
# samplesizes %>% unlist() %>% table() %>% sort()
samplesizes %>% unlist() %>% median()
samplesizes %>% unlist() %>% length()
# records_wide$Reliability[- (samplesizes %>% map_dbl(~ .[1]) %>% is.na() %>% which())]

samplesizes <- records_wide$Validity %>% str_match_all(regex("\\bn ?= ?(\\d+)", ignore_case = TRUE)) %>% map(~ as.numeric(.[,2]))
# samplesizes %>% unlist() %>% table()
samplesizes %>% unlist() %>% median()
# records_wide$Validity[- (samplesizes %>% map_dbl(~ .[1]) %>% is.na() %>% which())]

samplesizes <- records_wide$FactorAnalysis %>% str_match_all(regex("\\bn ?= ?(\\d+)", ignore_case = TRUE)) %>% map(~ as.numeric(.[,2]))
# samplesizes %>% unlist() %>% table()
samplesizes %>% unlist() %>% median()
# records_wide$FactorAnalysis[- (samplesizes %>% map_dbl(~ .[1]) %>% is.na() %>% which())]
```


## Number of factors

```{r}
records_wide$number_of_factors <- str_match_all(records_wide$FactorAnalysis, regex("(\\d+)(-| )factor", ignore_case = TRUE)) %>% map(~ as.numeric(.[,2]))
records_wide$number_of_factors_subscales <- str_match_all(records_wide$FactorsAndSubscales, ";") %>% map_dbl(~ length(.)) + 1
records_wide$number_of_factors_subscales[is.na(records_wide$FactorsAndSubscales)] <- NA_real_
# records_wide$FactorsAndSubscales %>% na.omit()
unlist(records_wide$number_of_factors) %>% table() %>% sort()
unlist(records_wide$number_of_factors_subscales) %>% table() %>% sort()
ggplot(records_wide, aes(number_of_factors_subscales)) + geom_bar(aes(y= ..count..), stat = 'count') + scale_x_continuous(breaks = 1:20)
cor(records_wide$number_of_factors_subscales, records_wide$number_of_factors %>% map_dbl(~ .[1]), use = 'p')
```


## Number of items

```{r}
records_wide$NumberOfTestItems <- str_replace_all(records_wide$NumberOfTestItems, "[[:space:]]+", " ")
item_numbers <- records_wide$NumberOfTestItems %>% str_match_all(regex("(\\d+)( |-)(total |primary |main |final )?(item|question)s?( ?-?measure)?", ignore_case = TRUE)) %>% map(~ as.numeric(.[,2]))
# table(unlist(item_numbers))
consists_of_numbers <- records_wide$NumberOfTestItems %>% str_match_all(regex("(comprises|consists of|contains|composed of|comprised of|) (\\d+)", ignore_case = TRUE)) %>% map(~ as.numeric(.[,3]))

just_numbers <- str_match(records_wide$NumberOfTestItems,pattern = "^(\\d+) ?$")[,2] %>% as.numeric()

median(unlist(item_numbers))

numbers <- records_wide$NumberOfTestItems %>% str_match_all("(\\d+)( |-)?") %>% map(~ as.numeric(.[,2]))

words <- case_when(
  str_detect(records_wide$NumberOfTestItems, regex("single(-| )(item|question)", ignore_case = TRUE)) ~ 1,
  str_detect(records_wide$NumberOfTestItems, regex("one(-| )(item|question)", ignore_case = TRUE)) ~ 1,
  str_detect(records_wide$NumberOfTestItems, regex("two(-| )(item|question)", ignore_case = TRUE)) ~ 2,
  str_detect(records_wide$NumberOfTestItems, regex("three(-| )(item|question)", ignore_case = TRUE)) ~ 3,
  str_detect(records_wide$NumberOfTestItems, regex("four(-| )(item|question)", ignore_case = TRUE)) ~ 4,
  str_detect(records_wide$NumberOfTestItems, regex("five(-| )(item|question)", ignore_case = TRUE)) ~ 5,
  str_detect(records_wide$NumberOfTestItems, regex("six(-| )(item|question)", ignore_case = TRUE)) ~ 6,
  str_detect(records_wide$NumberOfTestItems, regex("seven(-| )(item|question)", ignore_case = TRUE)) ~ 7,
  str_detect(records_wide$NumberOfTestItems, regex("eight(-| )(item|question)", ignore_case = TRUE)) ~ 8,
  str_detect(records_wide$NumberOfTestItems, regex("nine(-| )(item|question)", ignore_case = TRUE)) ~ 9,
  str_detect(records_wide$NumberOfTestItems, regex("ten(-| )(item|question)", ignore_case = TRUE)) ~ 10,
  str_detect(records_wide$NumberOfTestItems, regex("eleven(-| )(item|question)", ignore_case = TRUE)) ~ 11,
  str_detect(records_wide$NumberOfTestItems, regex("twelve(-| )(item|question)", ignore_case = TRUE)) ~ 12,
  str_detect(records_wide$NumberOfTestItems, regex("thirteen(-| )(item|question)", ignore_case = TRUE)) ~ 13,
  str_detect(records_wide$NumberOfTestItems, regex("fourteen(-| )(item|question)", ignore_case = TRUE)) ~ 14,
  str_detect(records_wide$NumberOfTestItems, regex("fifteen(-| )(item|question)", ignore_case = TRUE)) ~ 15,
  str_detect(records_wide$NumberOfTestItems, regex("sixteen(-| )(item|question)", ignore_case = TRUE)) ~ 16,
  str_detect(records_wide$NumberOfTestItems, regex("seventeen(-| )(item|question)", ignore_case = TRUE)) ~ 17,
  str_detect(records_wide$NumberOfTestItems, regex("eighteen(-| )(item|question)", ignore_case = TRUE)) ~ 18,
  str_detect(records_wide$NumberOfTestItems, regex("nineteen(-| )(item|question)", ignore_case = TRUE)) ~ 19,
  str_detect(records_wide$NumberOfTestItems, regex("twenty(-| )(item|question)", ignore_case = TRUE)) ~ 20,
  str_detect(records_wide$NumberOfTestItems, regex("forty(-| )(item|question)", ignore_case = TRUE)) ~ 40,
  str_detect(records_wide$NumberOfTestItems, regex("sex items", ignore_case = TRUE)) ~ 6,
  TRUE ~ NA_real_)

words_without_item <- case_when(
  str_detect(records_wide$NumberOfTestItems, regex("single", ignore_case = TRUE)) ~ 1,
  str_detect(records_wide$NumberOfTestItems, regex("one", ignore_case = TRUE)) ~ 1,
  str_detect(records_wide$NumberOfTestItems, regex("two", ignore_case = TRUE)) ~ 2,
  str_detect(records_wide$NumberOfTestItems, regex("three", ignore_case = TRUE)) ~ 3,
  str_detect(records_wide$NumberOfTestItems, regex("four", ignore_case = TRUE)) ~ 4,
  str_detect(records_wide$NumberOfTestItems, regex("five", ignore_case = TRUE)) ~ 5,
  str_detect(records_wide$NumberOfTestItems, regex("six", ignore_case = TRUE)) ~ 6,
  str_detect(records_wide$NumberOfTestItems, regex("seven", ignore_case = TRUE)) ~ 7,
  str_detect(records_wide$NumberOfTestItems, regex("eight", ignore_case = TRUE)) ~ 8,
  str_detect(records_wide$NumberOfTestItems, regex("nine", ignore_case = TRUE)) ~ 9,
  str_detect(records_wide$NumberOfTestItems, regex("ten", ignore_case = TRUE)) ~ 10,
  str_detect(records_wide$NumberOfTestItems, regex("eleven", ignore_case = TRUE)) ~ 11,
  str_detect(records_wide$NumberOfTestItems, regex("twelve", ignore_case = TRUE)) ~ 12,
  str_detect(records_wide$NumberOfTestItems, regex("thirteen", ignore_case = TRUE)) ~ 13,
  str_detect(records_wide$NumberOfTestItems, regex("fourteen", ignore_case = TRUE)) ~ 14,
  str_detect(records_wide$NumberOfTestItems, regex("fifteen", ignore_case = TRUE)) ~ 15,
  str_detect(records_wide$NumberOfTestItems, regex("sixteen", ignore_case = TRUE)) ~ 16,
  str_detect(records_wide$NumberOfTestItems, regex("seventeen", ignore_case = TRUE)) ~ 17,
  str_detect(records_wide$NumberOfTestItems, regex("eighteen", ignore_case = TRUE)) ~ 18,
  str_detect(records_wide$NumberOfTestItems, regex("nineteen", ignore_case = TRUE)) ~ 19,
  str_detect(records_wide$NumberOfTestItems, regex("twenty", ignore_case = TRUE)) ~ 20,
  str_detect(records_wide$NumberOfTestItems, regex("thirty", ignore_case = TRUE)) ~ 30,
  str_detect(records_wide$NumberOfTestItems, regex("forty", ignore_case = TRUE)) ~ 40,
  str_detect(records_wide$NumberOfTestItems, regex("fifty", ignore_case = TRUE)) ~ 50,
  TRUE ~ NA_real_)

# table(words)
# table(words_without_item[which(words_without_item!=words)])

# records_wide$NumberOfTestItems[!is.na(words)]
# records_wide$NumberOfTestItems[which(item_numbers %>% map(~ .[1]) == 1192)]
# records_wide$NumberOfTestItems[which(item_numbers %>% map(~ length(.)) > 1)]

# table(records_wide$NumberOfTestItems) %>% sort() %>% tail(20)
# records_wide$NumberOfTestItems[which(!is.na(numbers %>% map(~ .[1])) & 
#                                        is.na(item_numbers %>% map(~ .[1])) & 
#                                        is.na(consists_of_numbers %>% map(~ .[1])) &
#                                        is.na(just_numbers %>% map(~ .[1])) &
#                                        is.na(words)
#                                      )]

# records_wide$NumberOfTestItems[which(!is.na(records_wide$NumberOfTestItems) & is.na(numbers %>% map(~ .[1])) & is.na(item_numbers %>% map(~ .[1])) & is.na(words))]
unlist(numbers) %>% table() %>% qplot() +scale_x_sqrt(limits = c(1,30))

good_guess <- coalesce(just_numbers, 
                       item_numbers %>% map_dbl(~ .[1]), 
                       words)
best_guess <- coalesce(just_numbers, 
                       item_numbers %>% map_dbl(~ .[1]), 
                       words, 
                       consists_of_numbers %>% map_dbl(~ .[1]),
                       words_without_item,
                       numbers %>% map_dbl(~ .[1]))
xtabs(~ is.na(best_guess) + is.na(records_wide$NumberOfTestItems))
xtabs(~ is.na(good_guess) + is.na(records_wide$NumberOfTestItems))
records_wide$number_of_test_items <- good_guess
records_wide$number_of_test_items_best_guess <- best_guess
records_wide$number_of_test_items_potential_subscales <- coalesce(item_numbers %>% map_dbl(~ length(.)), consists_of_numbers %>% map_dbl(~ length(.)), numbers %>% map_dbl(~ length(.)), 1) 
# records_wide$NumberOfTestItems[which(!is.na(records_wide$NumberOfTestItems) & is.na(best_guess))]
qplot(records_wide$number_of_test_items,binwidth = 1) + xlim(0,200) + theme_bw()
# table(records_wide$number_of_test_items) %>% sort()

cor(records_wide$first_reliability_match, records_wide$number_of_test_items, use = 'p')
ggplot(records_wide %>% filter(number_of_test_items <= 40, number_of_test_items > 0), aes(factor(number_of_test_items), first_reliability_match)) + geom_pointrange(fun.data = "mean_se", stat = "summary") + theme_bw()

ggplot(records_wide %>% filter(number_of_test_items <= 40, number_of_test_items > 0), aes(factor(number_of_test_items), if_else(first_reliability_match == .70, 1, 0))) + geom_pointrange(fun.data = "mean_se", stat = "summary") + theme_bw()
```

## Transform to PsycInfo ASCII names
```{r}
records_wide$NameOC <- records_wide$Name
records_wide$Name <- records_wide$NameOC
records_wide$Name <- str_to_lower(records_wide$Name)

records_wide <- records_wide %>% mutate(
  # psycinfo doesn't differentiate dashes
  # Name = Name_orig,
  # Name_orig = Name,
  name_psycinfo = str_replace_all(Name, "(–|—|─|－|－|─|-|‑|‑|-|–|—)", "-"),
  name_psycinfo = str_replace_all(name_psycinfo, "(’)", "'"),
  name_psycinfo = str_replace_all(name_psycinfo, "(\")", "'"),
  name_psycinfo = str_replace_all(name_psycinfo, "(“|”)", "'"),
  name_psycinfo = str_replace_all(name_psycinfo, "(  +)", " "),
  name_psycinfo = str_replace_all(name_psycinfo, "( )", " "),
  name_psycinfo = str_replace_all(name_psycinfo, "(\n)", " "),
  name_psycinfo = str_replace_all(name_psycinfo, "ҫ", "c"),
  name_psycinfo = str_replace_all(name_psycinfo, "™", "(TM)"),
  name_psycinfo = str_replace_all(name_psycinfo, "©", "(C)"),
  name_psycinfo = str_replace_all(name_psycinfo, "®", "(R)"),
  name_psycinfo = coalesce(stringi::stri_trans_general(name_psycinfo, "latin-ascii"), name_psycinfo),
  name_psycinfo = str_replace_all(name_psycinfo, "\\(TM\\)", "™"),
  name_psycinfo = str_replace_all(name_psycinfo, "\\(C\\)", "©"),
  name_psycinfo = str_replace_all(name_psycinfo, "\\(R\\)", "®"),
  # name_psycinfo = coalesce(iconv(name_psycinfo, to='ASCII//TRANSLIT//IGNORE'), name_psycinfo),
  name_psycinfo = str_replace_all(name_psycinfo, "[:space:]+", " ")
)

psycinfo_chars <- c(" ", "-", ",", ";", ":", "!", "?", ".", "'", "(", ")", "[", 
"]", "/", "&", "©", "®", "+", "<", ">", "−", "0", "1", "2", 
"3", "4", "5", "6", "7", "8", "9", "a", "b", "c", "d", "e", "f", 
"g", "h", "i", "j", "k", "l", "m", "n", "o", "p", "q", "r", "s", 
"t", "™", "u", "v", "w", "x", "y", "z")
psycinfo_chars_escaped <- c(" ", "\\-", ",", ";", ":", "!", "?", ".", "'", "(", ")", "\\[", 
"\\]", "/", "&", "©", "®", "+", "<", ">", "−", "0", "1", "2", 
"3", "4", "5", "6", "7", "8", "9", "a", "b", "c", "d", "e", "f", 
"g", "h", "i", "j", "k", "l", "m", "n", "o", "p", "q", "r", "s", 
"t", "™", "u", "v", "w", "x", "y", "z")

records_wide %>% select(DOI, NameOC, Name, name_psycinfo) %>% 
  saveRDS("../sober_rubric/raw_data/psycinfo_psyctests_names.rds")
records_wide %>% group_by(name_psycinfo) %>%
  filter(n_distinct(Name) > 1) %>%
  arrange(name_psycinfo) %>%
  select(name_psycinfo, Name) %>% 
  nrow()


# records_wide %>% filter(Name != name_psycinfo, str_detect(name_psycinfo, regex(paste0("^[", paste0(psycinfo_chars_escaped, collapse = ""),"]+$"), ignore_case = T), negate = T)) %>% select(DOI, Name, name_psycinfo) %>% 
  # mutate(notascii = str_extract_all(name_psycinfo, regex(paste0("^[", paste0(psycinfo_chars_escaped, collapse = ""),"]+$"), ignore_case = T))) %>% 
  # View

#merged_ebsco %>% group_by(DOI) %>% filter(n()>1) %>% ungroup() %>% select(DOI) %>% distinct() %>% 
#  inner_join(
#    records_wide %>% filter(name_psycinfo != Name) %>% select(DOI, NameOC, name_psycinfo, Name)) %>% View
```

## Simplify lexically identical
```{r}

library(fuzzyjoin)
records_wide %>% distinct(Name) %>% pull(Name) %>% str_match_all("([^a-zA-Z0-9 ])") %>% unlist() %>% table() %>% sort()
records_wide <- records_wide %>% mutate(
  # psycinfo doesn't differentiate dashes
  # Name = Name_orig,
  # Name_orig = Name,
  Name = str_replace_all(Name, "(–|—|─|－|－|─|-|‑|‑|-|–|—)", "-"),
  Name = str_replace_all(Name, "(’)", "'"),
  Name = str_replace_all(Name, "(\")", "'"),
  Name = str_replace_all(Name, "(“|”)", "'"),
  Name = str_replace_all(Name, "(  +)", " "),
  Name = str_replace_all(Name, "ҫ", "c"),
  Name = str_replace_all(Name, "( )", " "),
  Name = str_replace_all(Name, "(\n)", " "),
  Name = str_replace_all(Name, "(™|©|®)", ""),
  Name = coalesce(stringi::stri_trans_general(Name, "latin-ascii"), Name),
  Name = str_replace_all(Name, "[:space:]+", " ")
)
library(tidylog)
crosswalk <- uk2us::ukus_crosswalk
crosswalk <- setNames(crosswalk$us, crosswalk$uk)
str_replace_all("a labour baulk", crosswalk)
records_wide <- records_wide %>% mutate(
  Name = str_replace_all(Name, crosswalk)
)

num_spelled <- tibble(
  num = as.character(0:100),
  spelled = c("zero", "one", "two", "three", "four", "five", "six", "seven", 
              "eight", "nine", "ten", "eleven", "twelve", "thirteen", 
              "fourteen", "fifteen", "sixteen", "seventeen", "eighteen", 
              "nineteen", "twenty", "twenty one", "twenty two", "twenty three",
              "twenty four", "twenty five", "twenty six", "twenty seven",
              "twenty eight", "twenty nine", "thirty", "thirty one", "thirty two",
              "thirty three", "thirty four", "thirty five", "thirty six",
              "thirty seven", "thirty eight", "thirty nine", "forty", "forty one",
              "forty two", "forty three", "forty four", "forty five", "forty six",
              "forty seven", "forty eight", "forty nine", "fifty", "fifty one",
              "fifty two", "fifty three", "fifty four", "fifty five", "fifty six",
              "fifty seven", "fifty eight", "fifty nine", "sixty", "sixty one",
              "sixty two", "sixty three", "sixty four", "sixty five", "sixty six",
              "sixty seven", "sixty eight", "sixty nine", "seventy", "seventy one",
              "seventy two", "seventy three", "seventy four", "seventy five",
              "seventy six", "seventy seven", "seventy eight", "seventy nine",
              "eighty", "eighty one", "eighty two", "eighty three", "eighty four",
              "eighty five", "eighty six", "eighty seven", "eighty eight", "eighty nine",
              "ninety", "ninety one", "ninety two", "ninety three", "ninety four",
              "ninety five", "ninety six", "ninety seven", "ninety eight", "ninety nine", "one hundred")
) 
roman_num_spelled <- tibble(num = c("\\bii\\b", "\\biii\\b", " \\biv\\b", "\\bv\\b"), 
                            spelled = c("two", "three", "four", "five"))
num_spelled <- bind_rows(num_spelled, roman_num_spelled)%>% arrange(desc(num))
replace_nums <- num_spelled$spelled
names(replace_nums) <- num_spelled$num

records_wide <- records_wide %>% mutate(
  # shouldn't treat 12 as being close to 1
  Name_comparable = str_replace_all(Name, "(-|,)", " "),
  Name_comparable = str_replace_all(Name_comparable, replace_nums),
)
```


## Get original test for revisions/translations

```{r}
get_original <- function(your_list) {
  if(is_empty(your_list)) {
    NA_character_
  } else {
    versions <- tibble(OtherVersion = your_list)
    versions <- versions %>%
      unnest_wider(OtherVersion) %>%
      mutate(
        OtherVersionTestName = map_chr(OtherVersionTestName, ~.x[[1]]),
        OtherVersionType = map_chr(OtherVersionTypeList, ~.x$OtherVersionType[[1]])
      ) %>%
      select(OtherVersionTestName, OtherVersionType)
    
    versions <- versions %>% 
      filter(OtherVersionType == "Original")
    
    if(nrow(versions) == 0) { 
      NA_character_ 
    } else {
      versions %>% pull(OtherVersionTestName)
      } 
  }
}
# debug(get_original)


records_wide <- records_wide %>% 
  hoist(OtherVersionList, original_name = list(), .transform = 
          get_original)

get_original_doi <- function(your_list) {
  if(is_empty(your_list)) {
    NA_character_
  } else {
    versions <- tibble(OtherVersion = your_list) %>% 
      rowwise() %>% 
      mutate(OtherVersionID = attr(OtherVersion, "OtherVersionTestID")) %>% 
      ungroup() %>% 
      unnest_wider(OtherVersion) %>%
      mutate(
        OtherVersionTestName = map_chr(OtherVersionTestName, ~.x[[1]]),
        OtherVersionType = map_chr(OtherVersionTypeList, ~.x$OtherVersionType[[1]])
      ) %>%
      select(OtherVersionID, OtherVersionTestName, OtherVersionType) %>% 
      mutate(OtherVersionDOI = str_replace(OtherVersionID, "9999-", "10.1037/t"))
    
    versions <- versions %>% 
      filter(OtherVersionType == "Original")
    
    if(nrow(versions) == 0) { 
      NA_character_ 
    } else {
      versions %>% pull(OtherVersionDOI)
      } 
  }
}
# debug(get_original)


records_wide <- records_wide %>% 
  hoist(OtherVersionList, original_DOI = list(), .transform = 
          get_original_doi)


records_wide <- records_wide %>% 
  mutate(original_DOI = as.character(original_DOI)) %>% 
  # hoist(original_DOI, original_DOI = list(1)) %>% 
  mutate(original_test_DOI = coalesce(original_DOI, DOI))

records_wide <- records_wide %>% 
  hoist(TestTypeList, test_type = list(1,1,1), .remove = FALSE)
xtabs(~ is.na(original_DOI) + test_type, records_wide)

n_distinct(records_wide$original_test_DOI)
```


## Get basis name without version/abbreviation/language
```{r}
records_wide$Name_base <- get_name_base(records_wide$Name)
# reduction
n_distinct(records_wide$Name) - n_distinct(records_wide$Name_base)

records_wide %>% filter(Name != Name_base) %>% nrow()
records_wide %>% group_by(test_type) %>% summarise(mismatch = sum(Name != Name_base)/n(), match = sum(Name == Name_base)/n())
```


```{r}
# records_wide %>% filter(test_type != "Original", is.na(original_DOI)) %>% select(DOI, Name_base, Name) %>% 
#   left_join(records_wide %>% filter(test_type == "Original") %>% select(Name_base = Name, original_DOI_by_name = DOI), by = "Name_base") %>% View

matches_by_doi <- records_wide %>% 
  select(original_DOI, Name, Name_base) %>% 
  inner_join(records_wide %>% 
               select(original_DOI = DOI, original_name = Name, original_Name_base = Name_base))

nrow(matches_by_doi)
# matches_by_doi %>% filter(original_name == Name_base)
# matches_by_doi %>% filter(original_name != Name_base) %>% View()
# matches_by_doi %>% filter(original_name != Name_base) %>% filter(str_detect(Name_base, " for "), str_match(Name_base, "^(.+) for .+$")[,2] == original_name) %>% pull(Name_base) %>% str_extract(" for .+$") %>% table() %>% sort() %>% names() %>% dput() 

unmatched_by_name <- records_wide %>% filter(is.na(original_DOI), test_type != "Original" | Name != Name_base) %>% select(test_type, DOI, Name = Name_base, NameOC_1 = NameOC) %>% anti_join(records_wide %>% filter(test_type == "Original") %>% select(Name)) 
nrow(unmatched_by_name)

matches_by_name <- records_wide %>% 
  filter(test_type != "Original" | Name != Name_base) %>% 
  select(test_type, DOI, Name = Name_base, NameOC_1 = NameOC, original_DOI) %>% 
  inner_join(records_wide %>% filter(test_type == "Original") %>% 
               select(original_DOI_by_name = DOI, Name, NameOC) %>% group_by(Name) %>% mutate(same_name_n = n()) %>% ungroup(), by = "Name") %>% 
  left_join(records_wide %>% filter(test_type == "Original") %>% 
               select(original_DOI = DOI, Name, NameOC_by_doi = NameOC), by = "original_DOI")

matches_by_name %>% group_by(original_DOI == original_DOI_by_name) %>% summarise(n())
# mismatches are mostly brE/amE equivalents and confusions between scale/measure/instrument and plural/singular
# matches_by_name %>% filter(original_DOI != original_DOI_by_name, NameOC != NameOC_by_doi) %>% 
#   select(NameOC_1, NameOC, NameOC_by_doi, same_name_n) %>% 
#   View()


sum(!is.na(records_wide$original_DOI))
records_wide <- records_wide %>% 
  left_join(records_wide %>% filter(test_type == "Original") %>% 
               select(original_DOI_by_name = DOI, Name) %>% group_by(Name) %>% filter(n() == 1) %>% ungroup(), by = c("Name_base" = "Name")) %>% 
  mutate(original_DOI_combined = coalesce(original_DOI, 
                                          if_else(test_type != "Original" &
                                                    Name != Name_base, original_DOI_by_name, NA_character_)))
sum(!is.na(records_wide$original_DOI_combined)) - sum(!is.na(records_wide$original_DOI))
```


## Index terms
```{r}
index_terms <- records_wide %>% select(IndexTermList) %>% 
  unlist()
table(index_terms) %>% sort() %>% tail(100)
```


## Subdisciplines
```{r}

classifications <- readr::read_tsv(col_names = T,
"code	classification
5000	Addiction, Gambling, and Substance Abuse/Use
5100	Anxiety and Depression
5200	Aptitude and Achievement
5300	Attitudes, Interests, Values, and Expectancies
5400	Cognitive Processes, Memory, and Decision Making
5500	Communication, Language, and Verbal Processing
5600	Consumer Behavior, Marketing, and Advertising
5700	Culture, Racial, and Ethnic Identity
5800	Development and Aging
5900	Education, Teaching, and Student Characteristics
6000	Emotional States, Emotional Responses, and Motivation
6100	Family Relationships and Parenting
6200	Functional Status and Adaptive Behavior
6300	Human Factors and Environmental Engineering
6400	Human-Computer Interaction
6500	Intelligence
6600	Legal and Forensic Evaluation
6700	Mental Health/Illness Related Assessment
6800	Military Personnel, Adjustment, and Training
6900	Neuropsychological Assessment
7000	Organizational, Occupational, and Career Development
7100	Perceptual, Motor, and Sensory Processing
7200	Personality
7300	Physical Health/Illness Related Assessment
7400	Religious and Political Beliefs
7500	Sex, Gender Roles, and Sexual Behavior
7600	Social, Group, and Interpersonal Relationships
7700	Sports, Recreation, and Leisure
7800	Trauma, Stress, and Coping
7900	Treatment, Rehabilitation, and Therapeutic Processes
8000	General Assessment Tools")

higher_class <- readr::read_tsv("classification	subdiscipline
Addiction, Gambling, and Substance Abuse/Use	Health and Clinical Psychology
Anxiety and Depression	Health and Clinical Psychology
Aptitude and Achievement	Educational and Developmental Psychology
Attitudes, Interests, Values, and Expectancies	Personality and Social Psychology
Cognitive Processes, Memory, and Decision Making	Cognitive Psychology
Communication, Language, and Verbal Processing	Cognitive Psychology
Consumer Behavior, Marketing, and Advertising	Industrial/Organizational Psychology
Culture, Racial, and Ethnic Identity	Personality and Social Psychology
Development and Aging	Educational and Developmental Psychology
Education, Teaching, and Student Characteristics	Educational and Developmental Psychology
Emotional States, Emotional Responses, and Motivation	Personality and Social Psychology
Family Relationships and Parenting	Personality and Social Psychology
Functional Status and Adaptive Behavior	Health and Clinical Psychology
Human Factors and Environmental Engineering	Industrial/Organizational Psychology
Human-Computer Interaction	Industrial/Organizational Psychology
Intelligence	Educational and Developmental Psychology
Legal and Forensic Evaluation	Health and Clinical Psychology
Mental Health/Illness Related Assessment	Health and Clinical Psychology
Military Personnel, Adjustment, and Training	Health and Clinical Psychology
Neuropsychological Assessment	Health and Clinical Psychology
Organizational, Occupational, and Career Development	Industrial/Organizational Psychology
Perceptual, Motor, and Sensory Processing	Cognitive Psychology
Personality	Personality and Social Psychology
Physical Health/Illness Related Assessment	Health and Clinical Psychology
Religious and Political Beliefs	Personality and Social Psychology
Sex, Gender Roles, and Sexual Behavior	Personality and Social Psychology
Social, Group, and Interpersonal Relationships	Personality and Social Psychology
Sports, Recreation, and Leisure	Personality and Social Psychology
Trauma, Stress, and Coping	Health and Clinical Psychology
Treatment, Rehabilitation, and Therapeutic Processes	Health and Clinical Psychology
General Assessment Tools	Health and Clinical Psychology")

classifications <- classifications %>% 
  left_join(higher_class)


records_wide <- records_wide %>% 
  left_join(higher_class %>% rename(subdiscipline_1 = subdiscipline), by = c("classification_1" = "classification")) %>% 
  left_join(higher_class %>% rename(subdiscipline_2 = subdiscipline), by = c("classification_2" = "classification"))

table(records_wide$subdiscipline_1 == records_wide$subdiscipline_2)
```


## Save
```{r}
saveRDS(records_wide, "../sober_rubric/raw_data/preprocessed_records.rds")
```
