---
title: "Construct proliferation"
author: "Ruben Arslan"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: "hide"
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = T, warning = T, message = T, fig.width = 8, fig.height = 4)

library(groundhog)
groundhog.library(c("tidyverse", "entropy", "ggrepel", "cowplot", "knitr", "readr",
                    "RColorBrewer", "plotly", "gglorenz", "rio", "hrbrthemes"), 
                  date = "2024-02-24")
theme_set(theme_minimal(base_size = 13))

colors <- RColorBrewer::brewer.pal(3, name = "Dark2")
names(colors) <- c("all", "novel", "constructs")

calc_norm_entropy <- function(n) {
  n <- n[n>0]
  entropy::entropy(n)/log(length(n))
}
```


<details><summary>Import</summary>
APA PsycTests

```{r}
records_wide <- readRDS("../sober_rubric/raw_data/preprocessed_records.rds")

records_wide %>% group_by(Name)  %>% filter(n()>1) %>% ungroup() %>% summarise(n_distinct(Name), n())

records_wide$first_construct <- str_trim(str_replace_all(str_to_lower(records_wide$first_construct), "[:space:]+", " "))
```

First EBSCO scrape of APA PsycInfo
```{r}
psycinfo <- read_tsv('../sober_rubric/raw_data/merged_table_all.tsv') %>% 
  # this tsv can be found in "Scraping-EBSCO-Host\data\merged tables"
#  mutate(Name = toTitleCase(Name)) %>% 
  rename(usage_count = "Hit Count") %>% 
  group_by(Name, Year) %>% 
  summarise(usage_count = sum(usage_count))
```


Second EBSCO scrape of APA PsycInfo
```{r}
overview <- readr::read_tsv("../sober_rubric/raw_data/20230617_ebsco_scrape_clean_overview_table_1.tsv")
byyear <- readr::read_tsv("../sober_rubric/raw_data/20230617_ebsco_scrape_table_years_1.tsv")
n_distinct(byyear$DOI)

overview %>% filter(is.na(Hits)) %>% nrow()
nrow(overview)
overview %>% filter(Hits >= 1) %>% nrow()

one_hit_wonders <- overview %>% filter(Hits == 1) %>% 
  mutate(Year = first_pub_year)

nrow(one_hit_wonders)
# for some few, the call was repeated by year for some reason
# one_hit_wonders %>% select(DOI, first_pub_year) %>% inner_join(byyear, by = "DOI") %>% arrange(DOI)

byyear <- byyear %>% anti_join(one_hit_wonders, by = "DOI")

all <- one_hit_wonders %>% 
  select(DOI, Year, Hits) %>% 
  bind_rows(byyear) %>% 
  left_join(overview %>% rename(total_hits = Hits), by = "DOI")

n_distinct(all$DOI)
all %>% filter(Hits > 0) %>% filter(Year < first_pub_year | Year > last_pub_year) %>% nrow()
all %>% group_by(total_hits, DOI) %>% summarise(hits_by_year = sum(Hits, na.rm = T)) %>% filter(hits_by_year > total_hits) %>% ungroup() %>% select(DOI, everything()) %>% mutate(diff = hits_by_year - total_hits) %>% nrow()
# all %>% group_by(total_hits, DOI) %>% summarise(hits_by_year = sum(usage_count, na.rm = T)) %>% filter(hits_by_year < total_hits) %>% select(DOI, everything()) %>% mutate(diff = hits_by_year - total_hits) %>%  View()
all %>% group_by(total_hits, DOI) %>% summarise(hits_by_year = sum(Hits, na.rm = T)) %>% filter(hits_by_year == total_hits) %>% nrow()
all %>% group_by(DOI) %>% summarise(hits_by_year = sum(Hits, na.rm = T)) %>% filter(hits_by_year == 0)
all %>% group_by(total_hits, DOI) %>% summarise(hits_by_year = sum(Hits, na.rm = T)) %>% filter(is.na(total_hits)) %>% pull(hits_by_year) %>% table()

psyctests_info <- records_wide %>% 
  select(DOI, TestYear, Name, first_construct, 
         original_test_DOI, original_DOI_combined, 
         test_type, ConstructList, subdiscipline_1, subdiscipline_2, 
         classification_1, classification_2, instrument_type_broad, 
         InstrumentType,
         number_of_factors_subscales, Name_base) %>%
  distinct() %>% 
  inner_join(all, by = c("DOI" = "DOI"), multiple = "all") %>% 
  rename(usage_count = "Hits")


write_rds(psyctests_info, "../sober_rubric/raw_data/psyctests_info.rds")
```

</details>

# 2016 changes in standards
```{r}
test_data <- records_wide %>%
  filter(TestYear <= 2022) %>%
    rowwise() %>%
    mutate(Methodology = length(MethodologyList) >0) %>%
    mutate(AdministrationMethod = length(AdministrationMethodList) >0) %>%
    mutate(PopulationGroup = length(PopulationGroupList) >0) %>%
    mutate(AgeGroup = length(AgeGroupList) >0) %>%
    group_by(TestYear) %>%
    summarise(Reliability = mean(Reliability!="No reliability indicated."),
              FactorAnalysis = mean(FactorAnalysis!="No factor analysis indicated."),
              # Unidimensional = mean(FactorAnalysis=="This is a unidimensional measure."),
              FactorsAndSubscales = mean(!is.na(FactorsAndSubscales)),
              Validity = mean(Validity!="No validity indicated."),
              Format = mean(!is.na(Format)),
              # Fee = mean(Fee == "Yes"),
              Methodology = mean(Methodology),
              AdministrationMethod = mean(AdministrationMethod),
              # AgeGroup = mean(AgeGroup),
              # PopulationGroup = mean(PopulationGroup),
              TestItems = mean(TestItemsAvailable == "Yes")) %>%
    pivot_longer(-TestYear)
test_data %>%
  ggplot(aes(TestYear, value, color = name)) +
  geom_vline(xintercept = 2016, linetype = 'dashed') +
  geom_line() +
  scale_x_continuous("Publication year in APA PsycTests",
                     limits = c(1993, 2030),
                     breaks = seq(1993, 2022, by = 1),
                     labels = c(1993, "", "", "", "", 1998, "", "", "", "", 2003, "", "", "", "", 2008, "", "", "", "", 2013, "", "", "", "", 2018, "", "", "", "2022"),
                     expand = expansion(add = c(0, 1.2))) +
  scale_color_brewer(type = "qual", guide = "none", palette = 2) +
  geom_text_repel(
    data = test_data %>% drop_na() %>% group_by(name) %>% filter(TestYear == max(TestYear, na.rm = T)),
    aes(label = name),
    segment.color = 'grey',
    xlim = c(2022, 2033),
    box.padding = 0.1,
    # point.padding = 0.6,
    nudge_x = 1.2,
    # nudge_y = 0,
    force = 0.5,
    hjust = 0,
    direction="y",
    na.rm = TRUE
  ) +
  ylab("PsycTests contains information about...") +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")
ggsave("figures/changed_standards_2016.pdf", width = 8, height = 4)
ggsave("figures/changed_standards_2016.png", width = 8, height = 4)
```


```{r}
records_wide %>% 
  group_by(TestYear) %>% 
  summarise(number_of_test_items = mean(number_of_test_items, na.rm = T)) %>% 
  filter(TestYear >= 1993, TestYear <= 2022) %>% 
ggplot(aes(TestYear, number_of_test_items)) + 
  geom_vline(xintercept = 2016, linetype = 'dashed') +
  geom_line() +
  scale_x_continuous("Publication year in APA PsycTests",
                     limits = c(1993, NA), 
                     breaks = seq(1993, 2022, by = 1),
                     labels = c(1993, "", "", "", "", 1998, "", "", "", "", 2003, "", "", "", "", 2008, "", "", "", "", 2013, "", "", "", "", 2018, "", "", "", "2022")) +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none") +
  xlab("Publication year in APA PsycTests") +
  ylab("Number of items in measure")
```


```{r}
records_wide %>% 
  filter(TestYear >= 1993, TestYear <= 2022) %>% 
ggplot(aes(TestYear, number_of_factors_subscales)) + 
  geom_vline(xintercept = 2016, linetype = 'dashed') +
  geom_pointrange(stat = 'summary', fun.data = 'mean_se') +
  xlim(1993, 2022) +
  xlab("Publication year in APA PsycTests") +
  ylab("Number of factors/subscales")
```


```{r}
records_wide %>% 
  group_by(InstrumentType, TestYear) %>% 
  summarise(tests = n()) %>% 
  group_by(TestYear) %>% 
  mutate(tests = tests/sum(tests, na.rm = T)) %>% 
  arrange(TestYear) %>% 
  filter(TestYear >= 1993, TestYear <= 2022) %>% 
  # mutate(tests = cumsum(tests)) %>% 
  ggplot(aes(TestYear, tests, color = InstrumentType)) + 
  geom_vline(xintercept = 2016, linetype = 'dashed') +
  scale_color_viridis_d() +
  geom_line() +
  xlim(1993, 2022) +
  xlab("Publication year in APA PsycTests") +
  ylab("Proportion of instrument type")
```


```{r}
records_wide %>% 
  # filter(instrument_type_broad !=)
  group_by(instrument_type_broad, TestYear) %>% 
  summarise(tests = n()) %>% 
  group_by(TestYear) %>% 
  mutate(tests = tests/sum(tests, na.rm = T)) %>% 
  arrange(TestYear) %>% 
  filter(TestYear >= 1993, TestYear <= 2022) %>% 
  # mutate(tests = cumsum(tests)) %>% 
  ggplot(aes(TestYear, tests, color = instrument_type_broad)) + 
  geom_vline(xintercept = 2016, linetype = 'dashed') +
  geom_line() +
  xlim(1993, 2022) +
  xlab("Publication year in APA PsycTests") +
  ylab("Proportion of instrument type")
```


```{r}
records_wide %>% 
  filter(instrument_type_broad != "questionnaire") %>% 
  group_by(InstrumentType, TestYear) %>% 
  summarise(tests = n()) %>% 
  group_by(TestYear) %>% 
  mutate(tests = tests/sum(tests, na.rm = T)) %>% 
  arrange(TestYear) %>% 
  filter(TestYear >= 1993, TestYear <= 2022) %>% 
  # mutate(tests = cumsum(tests)) %>% 
  ggplot(aes(TestYear, tests, color = InstrumentType)) + 
  geom_vline(xintercept = 2016, linetype = 'dashed') +
  geom_line() +
  xlim(1993, 2022) +
  xlab("Publication year in APA PsycTests") +
  ylab("Proportion of instrument type") +
  ggtitle("Without questionnaires")
```


```{r}
psyctests_info %>% group_by(DOI, TestYear) %>% 
  summarise(used = sum(usage_count, na.rm = T)) %>% 
  full_join(records_wide %>% select(DOI, TestYear)) %>% 
  mutate(used = coalesce(used, 0)) %>% 
  filter(TestYear >= 1993, TestYear <= 2022) %>% 
  group_by(TestYear) %>% 
  summarise(never_reused = mean(used == 0),
            used_once = mean(used == 1),
            used_twice = mean(used == 2),
            used_thrice = mean(used == 3),
            used_more_10 = mean(used > 9)) %>% 
  pivot_longer(-TestYear) %>% 
  ggplot(aes(TestYear, value, color = name)) + 
  geom_vline(xintercept = 2016, linetype = 'dashed') +
  geom_line() +
  xlim(1993, 2022) +
  xlab("Publication year in APA PsycTests") +
  ylab("Frequency")
```

# New measures by publication year
```{r}
count_all <- records_wide %>% 
  group_by(TestYear) %>% 
  summarise(tests = n()) %>% 
  arrange(TestYear)

count_orig <- records_wide %>% 
  filter(test_type == "Original") %>% 
  group_by(TestYear) %>% 
  summarise(tests = n()) %>% 
  arrange(TestYear)

count_base <- records_wide %>% 
  arrange(TestYear) %>% 
  distinct(Name_base, .keep_all = T) %>% 
  group_by(TestYear) %>% 
  summarise(tests = n_distinct(DOI))

count_construct <- records_wide %>% 
  arrange(TestYear) %>% 
  distinct(first_construct, .keep_all = T) %>% 
  group_by(TestYear) %>% 
  summarise(tests = n_distinct(first_construct)) %>% 
  arrange(TestYear)

counts <- bind_rows(
  "novel constructs" = count_construct,
  "novel measures" = count_orig,
  "with translations\n and revisions" = count_all,
  .id = "origin"
  ) %>% 
  rename(Year = TestYear) %>% 
  filter(Year <= 2022)


ggplot(counts, aes(Year, tests, color = origin)) + 
  geom_line() +
  geom_vline(xintercept = 2016, linetype = 'dashed') +
  scale_y_continuous("Number of measures/constructs published") +
  scale_x_continuous("Publication year in APA PsycTests",
                     limits = c(1993, 2030), 
                     breaks = seq(1993, 2022, by = 1),
                     labels = c(1993, "", "", "", "", 1998, "", "", "", "", 2003, "", "", "", "", 2008, "", "", "", "", 2013, "", "", "", "", 2018, "", "", "", "2022")) +
  scale_color_brewer(type = "qual", guide = "none", palette = 2) +
  # ggrepel::geom_text_repel(
  #   aes(label = str_replace(subdiscipline, " Psychology", "")), data = entropy_by_year %>% filter(Year == max(Year, na.rm = T)),
  #   size = 4, hjust = 1,
  #   ) + 
  geom_text_repel(aes(label = coalesce("  ", origin)), # This will force the correct position of the link's right end.
                  data = counts %>% drop_na() %>% group_by(origin) %>% filter(Year == max(Year, na.rm = T)),
                  segment.curvature = -0.1,
                  segment.square = TRUE,
                  segment.color = 'grey',
                  box.padding = 0.1,
                  point.padding = 0.6,
                  nudge_x = 1.5,
                  nudge_y = -15,
                  force = 0.5,
                  hjust = 0,
                  size = 3.3,
                  direction="y",
                  na.rm = F
  ) +
  geom_text_repel(data = counts %>% drop_na() %>% group_by(origin) %>% filter(Year == max(Year, na.rm = T)),
                  aes(label = paste0(" ", origin)),
                  segment.alpha = 0, ## This will 'hide' the link
                  segment.curvature = -0.1,
                  segment.square = TRUE,
                  lineheight = .9,
                  # segment.color = 'grey',
                  box.padding = 0.1,
                  point.padding = 0.6,
                  nudge_x = 1.2,
                  nudge_y = -15,
                  force = 1,
                  hjust = 0,
                  direction="y",
                  na.rm = F) +
   theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")

ggsave("figures/counts.pdf", width = 8, height = 4)
ggsave("figures/counts.png", width = 8, height = 4)
```



# Cumulative number of measures and constructs
```{r}
cumsum_all <- records_wide %>% 
  group_by(TestYear) %>% 
  summarise(tests = n()) %>% 
  arrange(TestYear) %>% 
  mutate(tests = cumsum(tests)) 

cumsum_orig <- records_wide %>% 
  filter(test_type == "Original") %>% 
  group_by(TestYear) %>% 
  summarise(tests = n()) %>% 
  arrange(TestYear) %>% 
  mutate(tests = cumsum(tests)) 

cumsum_base <- records_wide %>% 
  arrange(TestYear) %>% 
  distinct(Name_base, .keep_all = T) %>% 
  group_by(TestYear) %>% 
  summarise(tests = n_distinct(DOI)) %>% 
  mutate(tests = cumsum(tests)) 

cumsum_construct <- records_wide %>% 
  arrange(TestYear) %>% 
  distinct(first_construct, .keep_all = T) %>% 
  group_by(TestYear) %>% 
  summarise(tests = n_distinct(DOI)) %>% 
  arrange(TestYear) %>% 
  mutate(tests = cumsum(tests)) 

cumsums <- bind_rows(
  "novel constructs" = cumsum_construct,
  "novel measures" = cumsum_orig,
  "with translations\n and revisions" = cumsum_all,
  .id = "origin"
  ) %>% 
  rename(Year = TestYear) %>% 
  filter(Year <= 2022)


ggplot(cumsums, aes(Year, tests, color = origin)) + 
  geom_line() +
  geom_vline(xintercept = 2016, linetype = 'dashed') +
  scale_y_continuous("Cumulative number of measures") +
  scale_x_continuous("Publication year in APA PsycTests",
                     limits = c(1993, 2030), 
                     breaks = seq(1993,2022, by = 1),
                     labels = c(1993, "", "", "", "", 1998, "", "", "", "", 2003, "", "", "", "", 2008, "", "", "", "", 2013, "", "", "", "", 2018, "", "", "", "2022"),
                     expand = expansion(add = c(0, 1))) +
  scale_color_brewer(type = "qual", guide = "none", palette = 2) +
  # ggrepel::geom_text_repel(
  #   aes(label = str_replace(subdiscipline, " Psychology", "")), data = entropy_by_year %>% filter(Year == max(Year, na.rm = T)),
  #   size = 4, hjust = 1,
  #   )  +
  geom_text_repel(data = cumsums %>% drop_na() %>% group_by(origin) %>% filter(Year == max(Year, na.rm = T)),
                  aes(label = paste0(" ", origin, "\n (n = ", tests, ")")),
                  segment.square = TRUE,
                  lineheight = .9,
                  segment.color = 'grey',
                  nudge_x = 1.2,
                  hjust = 0,
                  na.rm = TRUE)+
   # theme_minimal(base_size = 13) +
   theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")  +
    guides(
    x = guide_axis(cap = "both"), # Cap both ends
  )
ggsave("figures/cumsums.pdf", width = 8, height = 4)
ggsave("figures/cumsums.png", width = 8, height = 4)
```

## By subdiscipline
```{r fig.width=8,fig.height=7}
cumsum_all <- records_wide %>% 
  group_by(subdiscipline_1, TestYear) %>% 
  summarise(tests = n()) %>% 
  arrange(TestYear) %>% 
  mutate(tests = cumsum(tests)) 


cumsum_orig <- records_wide %>% 
  filter(test_type == "Original") %>% 
  group_by(subdiscipline_1, TestYear) %>% 
  summarise(tests = n()) %>% 
  arrange(TestYear) %>% 
  mutate(tests = cumsum(tests)) 

cumsum_base <- records_wide %>% 
  arrange(TestYear) %>% 
  distinct(Name_base, .keep_all = T) %>% 
  group_by(subdiscipline_1, TestYear) %>% 
  summarise(tests = n_distinct(DOI)) %>% 
  mutate(tests = cumsum(tests)) 

cumsum_construct <- records_wide %>% 
  arrange(TestYear) %>% 
  distinct(first_construct, .keep_all = T) %>% 
  group_by(subdiscipline_1, TestYear) %>% 
  summarise(tests = n_distinct(DOI)) %>% 
  arrange(TestYear) %>% 
  mutate(tests = cumsum(tests)) 

cumsums <- bind_rows(
  "constructs" = cumsum_construct,
  "measures" = cumsum_orig,
  "with translations & revisions" = cumsum_all,
  .id = "origin"
  ) %>% 
  rename(Year = TestYear) %>% 
  filter(Year <= 2022)

cumsums$origin <- factor(cumsums$origin, levels = c("with translations & revisions", "constructs", "measures"))
my_colors <- c("with translations & revisions" = "#7570B3",
               "constructs" = "#1B9E77", 
               "measures" = "#D95F02") 

ggplot(cumsums, aes(Year, tests, color = origin)) + 
  geom_line() +
  facet_wrap(~ subdiscipline_1, scales = "free_y", ncol = 2) + 
  scale_y_continuous("Cumulative number of measures") +
  scale_x_continuous("Publication year in APA PsycTests",
                     limits = c(1993, 2022), 
                     breaks = seq(1993, 2022, by = 1),
                     labels = c(1993, "", "", "", "", 1998, "", "", "", "", 2003, "", "", "", "", 2008, "", "", "", "", 2013, "", "", "", "", 2018, "", "", "", "2022")) +
  scale_color_manual(values = my_colors, guide = guide_legend(title = NULL)) +
  theme_minimal(base_size = 13) +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = c(0.58, 0.08),
        legend.justification = c(0, 0),
        legend.box.just = "right",
        legend.text = element_text(size = 11))



ggsave("figures/cumsums_subdiscipline.pdf", width = 8, height = 7)
ggsave("figures/cumsums_subdiscipline.png", width = 8, height = 7)
```


# Tests by usage frequency
```{r}
test_frequency <- psyctests_info %>% 
  mutate(Test = if_else(test_type == "Original", DOI, original_test_DOI)) %>% 
  drop_na(Test) %>% 
  # filter(TestYear >= 1990) %>%
  filter(between(Year, 1993, 2022)) %>%
  group_by(Test) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  arrange(n)

test_frequency <- records_wide %>% 
  filter(test_type == "Original", TestYear <= 2022) %>% 
  select(Test = DOI) %>% 
  full_join(test_frequency) %>% 
  mutate(n = coalesce(n, 0.5))

test_frequency <- test_frequency %>% 
  group_by(n) %>% 
  summarise(count = n()) %>% 
  ungroup() %>% 
  mutate(percent = count/sum(count))

freq_plot <- ggplot(test_frequency, aes(n, count)) + 
  geom_bar(width = 0.1, fill = colors["novel"], stat = "identity") +
  # facet_wrap(~ subdiscipline_1, scales = "free_y") + 
  # scale_y_sqrt("Number of measures", breaks = c(0, 100, 400, 1000, 2000, 4000, 6000, 10000), limits = c(0, 11500)) +
  scale_y_continuous("Number of measures") +
  scale_x_log10("Usages recorded in APA PsycInfo 1993-2022",
                breaks = c(0.5, 1, 2, 5, 10, 100, 1000, 25000),
               labels = c(0, 1, 2, 5, 10, 100, 1000, 25000)) +
  
  geom_text(aes(label = if_else(n <= 2, sprintf("%.0f%%", percent*100), ""),
                x = n, y = count + 700)) +

  # scale_x_sqrt(breaks = c(0, 1, 2, 3, 4, 5, 10, 20, 40, 50), labels = c(0, 1, 2, 3, 4, 5, 10, 20, 40, "50+")) +
  # geom_text_repel(aes(x = n, label = first_acronym, y = y), 
  #                 data =
  #                   test_frequency %>% group_by(subdiscipline_1) %>% filter(row_number() > (n() - 10) ) %>% left_join(records_wide %>% select(Test = DOI, first_acronym)) %>% 
  #                   mutate(first_acronym = if_else(first_acronym == "HRSD", "HAM-D",
  #                                                  first_acronym)) %>% 
    # mutate(y = 20 + 50*(1+n()-row_number())),
    #               size = 3.3, force = 5, force_pull	= 0, max.time = 1, 
    #               max.overlaps = Inf,
    #               segment.color = "lightgray",
    #               segment.curvature = 1,
    #               hjust = 1,
    #               nudge_y = 10,
    #               direction = "y"
    # ) +
  theme_minimal(base_size = 13) +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")
freq_plot
ggsave("figures/frequency_across.pdf", width = 8, height = 4)
ggsave("figures/frequency_across.png", width = 8, height = 4)

test_frequency <- test_frequency %>% 
  filter(n >= 1) %>% 
  mutate(percent = count/sum(count))

freq_plot <- ggplot(test_frequency, aes(n, count)) + 
  geom_bar(width = 0.1, fill = colors["novel"], stat = "identity") +
  # scale_y_sqrt("Number of measures", breaks = c(0, 100, 400, 1000, 2000, 4000, 6000, 10000), limits = c(0, 11500)) +
  scale_y_continuous("Number of measures") +
  scale_x_log10("Usages recorded in APA PsycInfo 1993-2022",
                breaks = c(1, 2, 5, 10, 100, 1000, 25000),
               labels = c(1, 2, 5, 10, 100, 1000, 25000)) +
  
  geom_text(aes(label = if_else(n <= 2, sprintf("%.0f%%", percent*100), ""),
                x = n, y = count + 700)) +

  # scale_x_sqrt(breaks = c(0, 1, 2, 3, 4, 5, 10, 20, 40, 50), labels = c(0, 1, 2, 3, 4, 5, 10, 20, 40, "50+")) +
  # geom_text_repel(aes(x = n, label = first_acronym, y = y), 
  #                 data =
  #                   test_frequency %>% group_by(subdiscipline_1) %>% filter(row_number() > (n() - 10) ) %>% left_join(records_wide %>% select(Test = DOI, first_acronym)) %>% 
  #                   mutate(first_acronym = if_else(first_acronym == "HRSD", "HAM-D",
  #                                                  first_acronym)) %>% 
    # mutate(y = 20 + 50*(1+n()-row_number())),
    #               size = 3.3, force = 5, force_pull	= 0, max.time = 1, 
    #               max.overlaps = Inf,
    #               segment.color = "lightgray",
    #               segment.curvature = 1,
    #               hjust = 1,
    #               nudge_y = 10,
    #               direction = "y"
    # ) +
  theme_minimal(base_size = 13) +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")
freq_plot
ggsave("figures/frequency_across_no0.pdf", width = 8, height = 4)
ggsave("figures/frequency_across_no0.png", width = 8, height = 4)
```

```{r}
test_frequency <- psyctests_info %>% 
  mutate(Test = if_else(test_type == "Original", DOI, original_test_DOI)) %>% 
  drop_na(Test) %>% 
  # filter(TestYear >= 1990) %>%
  filter(between(Year, 1993, 2022)) %>%
  group_by(subdiscipline_1, Test) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  arrange(n)

test_frequency <- records_wide %>% 
  filter(test_type == "Original", TestYear <= 2022) %>% 
  select(subdiscipline_1, Test = DOI) %>% 
  full_join(test_frequency) %>% 
  mutate(n = coalesce(n, 0.5))

test_frequency <- test_frequency %>% 
  # mutate(n = if_else(n >= 1000, 1000, n)) %>% 
  mutate(subdiscipline_1 = str_replace(subdiscipline_1, " Psychology", "")) %>% 
  group_by(subdiscipline_1, n) %>% 
  summarise(count = n()) %>% 
  group_by(subdiscipline_1) %>% 
  mutate(percent = count/sum(count))

freq_plot <- ggplot(test_frequency, aes(n, count)) + 
  geom_bar(width = 0.1, fill = colors["novel"], stat = "identity") +
  facet_wrap(~ subdiscipline_1, scales = "free_y") + 
  # scale_y_sqrt("Number of measures", breaks = c(0, 100, 400, 1000, 2000, 4000, 6000, 10000), limits = c(0, 11500)) +
  scale_y_continuous("Number of measures", expand = expansion(c(0, 0.1))) +
  scale_x_log10("Usages recorded in APA PsycInfo 1993-2022",
                breaks = c(0.5, 1, 2, 10, 100, 1000, 25000),
               labels = c(0, 1, 2, 10, 100, 1000, 25000)) +
  
  geom_text(aes(label = if_else(n <= 2, sprintf("%.0f%%", percent*100), ""),
                x = n, y = count ), size = 3, vjust = -0.4, hjust = 0.4) +

  # scale_x_sqrt(breaks = c(0, 1, 2, 3, 4, 5, 10, 20, 40, 50), labels = c(0, 1, 2, 3, 4, 5, 10, 20, 40, "50+")) +
  # geom_text_repel(aes(x = n, label = first_acronym, y = y), 
  #                 data =
  #                   test_frequency %>% group_by(subdiscipline_1) %>% filter(row_number() > (n() - 10) ) %>% left_join(records_wide %>% select(Test = DOI, first_acronym)) %>% 
  #                   mutate(first_acronym = if_else(first_acronym == "HRSD", "HAM-D",
  #                                                  first_acronym)) %>% 
    # mutate(y = 20 + 50*(1+n()-row_number())),
    #               size = 3.3, force = 5, force_pull	= 0, max.time = 1, 
    #               max.overlaps = Inf,
    #               segment.color = "lightgray",
    #               segment.curvature = 1,
    #               hjust = 1,
    #               nudge_y = 10,
    #               direction = "y"
    # ) +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")

freq_plot
ggsave("figures/frequency.pdf", width = 8, height = 4)
ggsave("figures/frequency.png", width = 8, height = 4)

test_frequency <- test_frequency %>% 
  filter(n >= 1) %>% 
  group_by(subdiscipline_1) %>% 
  mutate(percent = count/sum(count))

freq_plot <- ggplot(test_frequency, aes(n, count)) + 
  geom_bar(width = 0.1, fill = colors["novel"], stat = "identity") +
  facet_wrap(~ subdiscipline_1, scales = "free_y") + 
  # scale_y_sqrt("Number of measures", breaks = c(0, 100, 400, 1000, 2000, 4000, 6000, 10000), limits = c(0, 11500)) +
    scale_y_continuous("Number of measures", expand = expansion(c(0, 0.1))) +
  scale_x_log10("Usages recorded in APA PsycInfo 1993-2022",
                breaks = c(1, 2, 5, 10, 100, 1000, 25000),
               labels = c(1, 2, 5, 10, 100, 1000, 25000)) +
  
  geom_text(aes(label = if_else(n <= 2, sprintf("%.0f%%", percent*100), ""),
                x = n, y = count ), size = 3, vjust = -0.11, hjust = 0.4) +

  # scale_x_sqrt(breaks = c(0, 1, 2, 3, 4, 5, 10, 20, 40, 50), labels = c(0, 1, 2, 3, 4, 5, 10, 20, 40, "50+")) +
  # geom_text_repel(aes(x = n, label = first_acronym, y = y), 
  #                 data =
  #                   test_frequency %>% group_by(subdiscipline_1) %>% filter(row_number() > (n() - 10) ) %>% left_join(records_wide %>% select(Test = DOI, first_acronym)) %>% 
  #                   mutate(first_acronym = if_else(first_acronym == "HRSD", "HAM-D",
  #                                                  first_acronym)) %>% 
    # mutate(y = 20 + 50*(1+n()-row_number())),
    #               size = 3.3, force = 5, force_pull	= 0, max.time = 1, 
    #               max.overlaps = Inf,
    #               segment.color = "lightgray",
    #               segment.curvature = 1,
    #               hjust = 1,
    #               nudge_y = 10,
    #               direction = "y"
    # ) +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")
freq_plot
ggsave("figures/frequency_no0.pdf", width = 8, height = 4)
```

## By instrument type
```{r}
usage_by_year_instrument_type <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  group_by(instrument_type_broad, Year, Test = DOI) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  group_by(instrument_type_broad) %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(instrument_type_broad, n_tests, Year) %>% 
  summarise(n = sum(n),
            diff_tests = n()) %>% 
  ungroup()



usage_by_year_instrument_type %>% 
  ggplot(., aes(Year, n, color = instrument_type_broad)) +
  geom_line(size = 0.7) +
  scale_y_continuous("Times tests were coded in PsycInfo") +
  scale_x_continuous(limits = c(1993, 2030), breaks = c(1993, 1998, 2003, 2008, 2013, 2018, 2022)) +
  scale_color_brewer(type = "qual", guide = "none", palette = 2) +
  # ggrepel::geom_text_repel(
  #   aes(label = str_replace(subdiscipline, " Psychology", "")), data = entropy_by_year %>% filter(Year == max(Year, na.rm = T)),
  #   size = 4, hjust = 1,
  #   ) + 
  geom_text_repel(aes(label = gsub("^.*$", " ", instrument_type_broad)), # This will force the correct position of the link's right end.
                  data = usage_by_year_instrument_type %>% filter(Year == max(Year, na.rm = T)),
                  segment.curvature = -0.1,
                  segment.square = TRUE,
                  segment.color = 'grey',
                  box.padding = 0.1,
                  point.padding = 0.6,
                  nudge_x = 0.15,
                  nudge_y = 0.05,
                  force = 0.5,
                  hjust = 0,
                  direction="y",
                  na.rm = TRUE
  ) +
  geom_text_repel(data = usage_by_year_instrument_type %>% filter(Year == max(Year, na.rm = T)),
                  aes(label = paste0("  ",str_replace(instrument_type_broad, " Psychology", ""), " (n=", n_tests, ")")),
                  segment.alpha = 0, ## This will 'hide' the link
                  segment.curvature = -0.1,
                  segment.square = TRUE,
                  # segment.color = 'grey',
                  box.padding = 0.1,
                  point.padding = 0.6,
                  nudge_x = 0.15,
                  nudge_y = 0.05,
                  force = 0.5,
                  hjust = 0,
                  direction="y",
                  na.rm = TRUE)+
  theme_minimal(base_size = 13) +
   theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")
ggsave("figures/usage_by_year_instrument_type.pdf", width = 10, height = 4)
ggsave("figures/usage_by_year_instrument_type.png", width = 10, height = 4)
```

```{r}
usage_by_year_instrument_type <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  group_by(InstrumentType, Year, Test = DOI) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  group_by(InstrumentType) %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(InstrumentType, n_tests, Year) %>% 
  summarise(n = sum(n),
            diff_tests = n()) %>% 
  ungroup()



usage_by_year_instrument_type %>% 
  ggplot(., aes(Year, n, color = InstrumentType)) +
  geom_line(size = 0.7) +
  scale_y_continuous("Times tests were coded in PsycInfo") +
  scale_x_continuous(limits = c(1993, 2035), breaks = c(1993, 1998, 2003, 2008, 2013, 2018, 2022)) +
  scale_color_discrete() +
  # ggrepel::geom_text_repel(
  #   aes(label = str_replace(subdiscipline, " Psychology", "")), data = entropy_by_year %>% filter(Year == max(Year, na.rm = T)),
  #   size = 4, hjust = 1,
  #   ) + 
  geom_text_repel(aes(label = gsub("^.*$", " ", InstrumentType)), # This will force the correct position of the link's right end.
                  data = usage_by_year_instrument_type %>% filter(Year == max(Year, na.rm = T)),
                  segment.curvature = -0.1,
                  segment.square = TRUE,
                  segment.color = 'grey',
                  box.padding = 0.1,
                  point.padding = 0.6,
                  nudge_x = 0.15,
                  nudge_y = 0.05,
                  force = 0.5,
                  hjust = 0,
                  direction="y",
                  na.rm = TRUE
  ) +
  geom_text_repel(data = usage_by_year_instrument_type %>% filter(Year == max(Year, na.rm = T)),
                  aes(label = paste0("  ",str_replace(InstrumentType, " Psychology", ""), " (n=", n_tests, ")")),
                  segment.alpha = 0, ## This will 'hide' the link
                  segment.curvature = -0.1,
                  segment.square = TRUE,
                  # segment.color = 'grey',
                  box.padding = 0.1,
                  point.padding = 0.6,
                  nudge_x = 0.15,
                  nudge_y = 0.05,
                  force = 0.5,
                  hjust = 0,
                  direction="y",
                  na.rm = TRUE)+
  theme_minimal(base_size = 13) +
   theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")
ggsave("figures/usage_by_year_instrument_type_narrow.pdf", width = 14, height = 10)
ggsave("figures/usage_by_year_instrument_type_narrow.png", width = 14, height = 10)
```

# Entropy

## Entropy by year
```{r}
byorig_entropy_by_year <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  mutate(Test = if_else(test_type == "Original", DOI, original_test_DOI)) %>% 
  drop_na(Test) %>% 
  group_by(Year, Test) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(entropy = entropy(n),
            norm_entropy = calc_norm_entropy(n),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()
# what's the point of mutate(n_tests = n_distinct(Test))? just to check?


byconstruct_entropy_by_year <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  drop_na(first_construct) %>% 
  group_by(Year, Test = first_construct) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(entropy = entropy(n),,
            norm_entropy = calc_norm_entropy(n),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()

all_entropy_by_year <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  drop_na(DOI) %>% 
  group_by(Year, Test = DOI) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(entropy = entropy(n),,
            norm_entropy = calc_norm_entropy(n),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()

original_entropy_by_year <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  filter(test_type == "Original") %>% 
  group_by(Year, Test = DOI) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(entropy = entropy(n),,
            norm_entropy = calc_norm_entropy(n),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()

entropy_by_year <- bind_rows(# "all tests" = all_entropy_by_year,
                             "measures" = original_entropy_by_year,
                             "with translations\n and revisions" = byorig_entropy_by_year,
                             # "by name base" = bybase_entropy_by_year,
                             "constructs" = byconstruct_entropy_by_year,
                             .id = "version")


entropy_by_year %>% 
  ggplot(., aes(Year, norm_entropy, color = version)) +
  geom_line(size = 0.7) +
  scale_y_continuous("Normalized Shannon Entropy", limits = c(0, 1), labels = scales::percent) +
  # geom_line(aes(y = log(n)), color = 'red') +
  scale_x_continuous("Usage year as coded in APA PsycInfo", limits = c(1993, 2030), 
                     breaks = seq(1993, 2022, by = 1),
                     labels = c(1993, "", "", "", "", 1998, "", "", "", "", 2003, "", "", "", "", 2008, "", "", "", "", 2013, "", "", "", "", 2018, "", "", "", "2022")) +
  scale_color_brewer(type = "qual", guide = "none", palette = 2) +
  geom_vline(xintercept = 2016, linetype = 'dashed') +
  # ggrepel::geom_text_repel(
  #   aes(label = str_replace(subdiscipline, " Psychology", "")), data = entropy_by_year %>% filter(Year == max(Year, na.rm = T)),
  #   size = 4, hjust = 1,
  #   ) + 
  geom_text_repel(data = entropy_by_year %>% drop_na() %>% group_by(version) %>% filter(Year == max(Year, na.rm = T)),
                  aes(label = paste0(" ",version)), # "\n (n = ", n_tests, ")"
                  segment.curvature = -0.5,
                  segment.square = TRUE,
                  segment.color = 'grey', 
                  xlim = c(2023, 2030),
                  nudge_x = 1.14,
                  lineheight = .9,
                  hjust = 0,
                  direction="y",
                  na.rm = TRUE) +
  theme_minimal(base_size = 13) +
   theme(
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")

ggsave("figures/entropy.pdf", width = 8, height = 4)
ggsave("figures/entropy.png", width = 8, height = 4)
```


## by subdiscipline

### all measures
```{r fig.width=8,fig.height=4}
entropy_by_year <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  group_by(subdiscipline_1, Year, Test = DOI) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  group_by(subdiscipline_1) %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(subdiscipline_1, n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(entropy = entropy(n),,
            norm_entropy = calc_norm_entropy(n),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()


entropy_by_year %>% 
  ggplot(., aes(Year, norm_entropy, color = subdiscipline_1)) +
  geom_line(size = 0.7) +
  scale_y_continuous("Normalized Shannon Entropy\n(with revisions and translations)", limits = c(0, 1), labels = scales::percent) +
  # geom_line(aes(y = log(n)), color = 'red') +
  scale_x_continuous("Usage year as coded in APA PsycInfo", limits = c(1993, 2033), 
                     breaks = seq(1993,2022, by = 1),
                     labels = c(1993, "", "", "", "", 1998, "", "", "", "", 2003, "", "", "", "", 2008, "", "", "", "", 2013, "", "", "", "", 2018, "", "", "", "2022"),
                     expand = expansion(add = c(0, 14))) +
  scale_color_brewer(type = "qual", guide = "none", palette = 2) +
  # ggtitle(str_c(n_distinct(tests_by_year$Test), " measures tracked in PsycInfo")) +
 # geom_text_repel(aes(label = gsub("^.*$", " ", subdiscipline_1)), # This will force the correct position of the link's right end.
 #                  data = entropy_by_year %>% drop_na() %>% group_by(subdiscipline_1) %>% filter(Year == max(Year, na.rm = T)),
 #                  segment.curvature = -0.1,
 #                  segment.square = TRUE,
 #                  segment.color = 'grey',
 #                  box.padding = 0.1,
 #                  point.padding = 0.6,
 #                  max.overlaps = Inf,
 #                  nudge_x = 1.3,
 #                  # nudge_y = 0,
 #                  force = 20,
 #                  hjust = 0,
 #                  direction="y",
 #                  na.rm = TRUE
 #  ) +  
  geom_text_repel(data = entropy_by_year %>% drop_na() %>% group_by(subdiscipline_1) %>% filter(Year == max(Year, na.rm = T)),
                  aes(label = paste0("  ",str_replace(subdiscipline_1, " Psychology", ""), " (n=", n_tests, ")")),
                  # segment.alpha = 0, ## This will 'hide' the link
                  segment.curvature = -0.1,
                  segment.square = TRUE,
                  segment.color = 'grey',
                  box.padding = 0.1,
                  max.overlaps = Inf,
                  point.padding = 0.6,
                  xlim = c(2022, NA),
                  nudge_x = 2,
                  # nudge_y = 0.0,
                  force = 5,
                  hjust = 0,
                  direction="y",
                  na.rm = F) +
  theme_minimal(base_size = 13) +
   theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none") +
    coord_cartesian(clip = "off")
ggsave("figures/entropy_subdiscipline_all.pdf", width = 8, height = 4)
ggsave("figures/entropy_subdiscipline_all.png", width = 8, height = 4)
```

### original measures
```{r fig.width=8,fig.height=4}
entropy_by_year <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  mutate(Test = if_else(test_type == "Original", DOI, original_test_DOI)) %>% 
  drop_na(Test) %>% 
  group_by(subdiscipline_1, Year, Test) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  group_by(subdiscipline_1) %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(subdiscipline_1, n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(entropy = entropy(n),,
            norm_entropy = calc_norm_entropy(n),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()


entropy_by_year %>% 
  ggplot(., aes(Year, norm_entropy, color = subdiscipline_1)) +
  geom_line(size = 0.7) +
  scale_y_continuous("Normalized Shannon Entropy\n(novel measures)", limits = c(0, 1), labels = scales::percent) +
  # geom_line(aes(y = log(n)), color = 'red') +
  scale_x_continuous("Usage year as coded in APA PsycInfo", limits = c(1993, 2030), 
                     breaks = seq(1993, 2022, by = 1),
                     labels = c(1993, "", "", "", "", 1998, "", "", "", "", 2003, "", "", "", "", 2008, "", "", "", "", 2013, "", "", "", "", 2018, "", "", "", "2022"),
                     expand = expansion(add = c(0, 17))) +
  scale_color_brewer(type = "qual", guide = "none", palette = 2) +
  # ggtitle(str_c(n_distinct(tests_by_year$Test), " measures tracked in PsycInfo")) +
 # geom_text_repel(aes(label = gsub("^.*$", " ", subdiscipline_1)), # This will force the correct position of the link's right end.
 #                  data = entropy_by_year %>% drop_na() %>% group_by(subdiscipline_1) %>% filter(Year == max(Year, na.rm = T)),
 #                  segment.curvature = -0.1,
 #                  segment.square = TRUE,
 #                  segment.color = 'grey',
 #                  box.padding = 0.1,
 #                  point.padding = 0.6,
 #                  max.overlaps = Inf,
 #                  nudge_x = 1.3,
 #                  # nudge_y = 0,
 #                  force = 20,
 #                  hjust = 0,
 #                  direction="y",
 #                  na.rm = TRUE
 #  ) +  
  geom_text_repel(data = entropy_by_year %>% drop_na() %>% group_by(subdiscipline_1) %>% filter(Year == max(Year, na.rm = T)),
                  aes(label = paste0("  ",str_replace(subdiscipline_1, " Psychology", ""), " (n=", n_tests, ")")),
                  # segment.alpha = 0, ## This will 'hide' the link
                  segment.curvature = -0.1,
                  segment.square = TRUE,
                  segment.color = 'grey',
                  box.padding = 0.1,
                  max.overlaps = Inf,
                  point.padding = 0.6,
                  xlim = c(2022, NA),
                  nudge_x = 2,
                  # nudge_y = 0.0,
                  force = 5,
                  hjust = 0,
                  direction="y",
                  na.rm = F)  +
   theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none") +
    coord_cartesian(clip = "off")
ggsave("figures/entropy_subdiscipline_orig.pdf", width = 8, height = 4)
ggsave("figures/entropy_subdiscipline_orig.png", width = 8, height = 4)
```
### constructs
```{r}
entropy_by_year <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  group_by(subdiscipline_1, Year, Test = first_construct) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  group_by(subdiscipline_1) %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(subdiscipline_1, n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(entropy = entropy(n),,
            norm_entropy = calc_norm_entropy(n),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()


entropy_by_year %>% 
  ggplot(., aes(Year, norm_entropy, color = subdiscipline_1)) +
  geom_line(size = 0.7) +
  scale_y_continuous("Normalized Shannon Entropy (constructs)", limits = c(0, 1), labels = scales::percent) +
  # geom_line(aes(y = log(n)), color = 'red') +
  scale_x_continuous("Usage year as coded in APA PsycInfo", limits = c(1993, 2038), 
                     breaks = seq(1993, 2022, by = 1),
                     labels = c(1993, "", "", "", "", 1998, "", "", "", "", 2003, "", "", "", "", 2008, "", "", "", "", 2013, "", "", "", "", 2018, "", "", "", "2022"),
                     expand = expansion(add = c(0, 10))) +
  scale_color_brewer(type = "qual", guide = "none", palette = 2) +
  # ggtitle(str_c(n_distinct(tests_by_year$Test), " measures tracked in PsycInfo")) +
  # ggrepel::geom_text_repel(
  #   aes(label = str_replace(subdiscipline, " Psychology", "")), data = entropy_by_year %>% filter(Year == max(Year, na.rm = T)),
  #   size = 4, hjust = 1,
  #   ) + 
  geom_text_repel(data = entropy_by_year %>% drop_na() %>% group_by(subdiscipline_1) %>% filter(Year == max(Year, na.rm = T)),
                  aes(label = paste0("  ",str_replace(subdiscipline_1, " Psychology", ""), " (n=", n_tests, ")")),
                  # segment.alpha = 0, ## This will 'hide' the link
                  segment.curvature = -0.1,
                  segment.square = TRUE,
                  segment.color = 'grey',
                  box.padding = 0.1,
                  max.overlaps = Inf,
                  point.padding = 0.6,
                  xlim = c(2022, NA),
                  nudge_x = 2,
                  # nudge_y = 0.0,
                  force = 5,
                  hjust = 0,
                  direction="y",
                  na.rm = F) +
   theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")
ggsave("figures/entropy_subdiscipline_constructs.pdf", width = 8, height = 4)
ggsave("figures/entropy_subdiscipline_constructs.png", width = 8, height = 4)
```

### By instrument type
```{r}
entropy_by_year <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  group_by(instrument_type_broad, Year, Test = DOI) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  group_by(instrument_type_broad) %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(instrument_type_broad, n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(entropy = entropy(n),
            norm_entropy = calc_norm_entropy(n),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()



entropy_by_year %>% 
  ggplot(., aes(Year, norm_entropy, color = instrument_type_broad)) +
  geom_line(size = 0.7) +
  scale_y_continuous("Normalized Shannon Entropy", limits = c(0, 1), labels = scales::percent) +
  # geom_line(aes(y = log(n)), color = 'red') +
  scale_x_continuous(limits = c(1993, 2027), breaks = c(1993, 1998, 2003, 2008, 2013, 2018, 2022)) +
  scale_color_brewer(type = "qual", guide = "none", palette = 3) +
  # ggrepel::geom_text_repel(
  #   aes(label = str_replace(subdiscipline, " Psychology", "")), data = entropy_by_year %>% filter(Year == max(Year, na.rm = T)),
  #   size = 4, hjust = 1,
  #   ) + 
  geom_text_repel(aes(label = gsub("^.*$", " ", instrument_type_broad)), # This will force the correct position of the link's right end.
                  data = entropy_by_year %>% filter(Year == max(Year, na.rm = T)),
                  segment.curvature = -0.1,
                  segment.square = TRUE,
                  segment.color = 'grey',
                  box.padding = 0.1,
                  point.padding = 0.6,
                  nudge_x = 0.15,
                  nudge_y = 0.05,
                  force = 0.5,
                  hjust = 0,
                  direction="y",
                  na.rm = TRUE
  ) +
  geom_text_repel(data = entropy_by_year %>% filter(Year == max(Year, na.rm = T)),
                  aes(label = paste0("  ",str_replace(instrument_type_broad, " Psychology", ""), " (n=", n_tests, ")")),
                  segment.alpha = 0, ## This will 'hide' the link
                  segment.curvature = -0.1,
                  segment.square = TRUE,
                  # segment.color = 'grey',
                  box.padding = 0.1,
                  point.padding = 0.6,
                  nudge_x = 0.15,
                  nudge_y = 0.05,
                  force = 0.5,
                  hjust = 0,
                  direction="y",
                  na.rm = TRUE)+
  theme_minimal(base_size = 13) +
   theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")
```


## Lorenz curves
```{r}
test_frequency <- psyctests_info %>% 
  mutate(Test = if_else(test_type == "Original", DOI, original_test_DOI)) %>% 
  drop_na(Test) %>% 
  # filter(TestYear >= 1990) %>%
  filter(between(Year, 1993, 2022)) %>%
  group_by(subdiscipline_1, Test) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  arrange(n) %>% 
  mutate(decile = Hmisc::cut2(n, g = 10)) %>% 
  mutate(cumsum = cumsum(n),
         sum = sum(n))
# 
# test_frequency %>% 
#     group_by(subdiscipline_1, decile) %>% 
#     summarise(share = sum(n)/first(sum),
#               median_n = median(n),
#               n_measures = n()) %>% 
#   View()


ggplot(test_frequency, aes(n)) +
  stat_lorenz(desc = F) +
  coord_fixed() +
  geom_abline(linetype = "dashed") +
      theme_minimal() +
    hrbrthemes::scale_x_percent("Cumulative percentage of measures") +
    hrbrthemes::scale_y_percent("Cumulative percentage of measure market share") #+
#    hrbrthemes::theme_ipsum_rc()

ggplot(test_frequency, aes(n, color = subdiscipline_1)) +
  stat_lorenz(desc = F) +
  coord_fixed() +
  geom_abline(linetype = "dashed") +
      theme_minimal() +
    hrbrthemes::scale_x_percent("Cumulative percentage of measures") +
    hrbrthemes::scale_y_percent("Cumulative percentage of measure market share")
```

# Robustness checks
```{r}
all_constructs_over_time <- records_wide %>% select(subdiscipline_1, DOI, TestYear, ConstructList) %>% 
    unnest(ConstructList) %>% 
    rowwise() %>% 
    mutate(construct = unlist(ConstructList)) %>% 
  select(-ConstructList)

cumsum_all_constructs <- all_constructs_over_time %>% 
  arrange(TestYear) %>% 
  distinct(construct, .keep_all = T) %>% 
  group_by(TestYear) %>% 
  summarise(constructs = n_distinct(construct)) %>% 
  arrange(TestYear) %>% 
  mutate(constructs = cumsum(constructs)) 


cumsum_construct <- records_wide %>% 
  arrange(TestYear) %>% 
  distinct(first_construct, .keep_all = T) %>% 
  group_by(TestYear) %>% 
  summarise(constructs = n_distinct(first_construct)) %>% 
  arrange(TestYear) %>% 
  mutate(constructs = cumsum(constructs))

cumsums <- bind_rows(
  "first constructs" = cumsum_construct,
  "all constructs" = cumsum_all_constructs,
  .id = "origin"
  ) %>% 
  rename(Year = TestYear) %>% 
  filter(Year <= 2022)


ggplot(cumsums, aes(Year, constructs, color = origin)) + 
  geom_line() +
  scale_y_continuous("Cumulative number of constructs") +
  scale_x_continuous("Publication year in APA PsycTests",
                     limits = c(1993, 2027), 
                     breaks = seq(1993, 2022, by = 1),
                     labels = c(1993, "", "", "", "", 1998, "", "", "", "", 2003, "", "", "", "", 2008, "", "", "", "", 2013, "", "", "", "", 2018, "", "", "", "2022")) +
  scale_color_brewer(type = "qual", guide = "none", palette = 2) +
  # ggrepel::geom_text_repel(
  #   aes(label = str_replace(subdiscipline, " Psychology", "")), data = entropy_by_year %>% filter(Year == max(Year, na.rm = T)),
  #   size = 4, hjust = 1,
  #   ) + 
  geom_text_repel(data = cumsums %>% drop_na() %>% group_by(origin) %>% filter(Year == max(Year, na.rm = T)),
                  aes(label = paste0(" ", origin, "\n (n = ", constructs, ")")),
                  segment.square = TRUE,
                  lineheight = .9,
                  segment.color = 'grey',
                  nudge_x = 1.2,
                  hjust = 0,
                  na.rm = TRUE)

ggsave("figures/cumsum_all_vs_first.pdf", width = 8, height = 4)
ggsave("figures/cumsum_all_vs_first.png", width = 8, height = 4)
```

## All or first constructs

For some 20% of tests, two or more constructs were coded. In most plots, we simply use
the first construct for each test.
```{r}
records_wide <- records_wide %>% 
  rowwise() %>% 
  mutate(constructs_n = length(ConstructList)) %>% 
  ungroup()

table(records_wide$constructs_n)
round(prop.table(table(records_wide$constructs_n)),2)

ggplot(records_wide, aes(constructs_n)) + 
  geom_bar()
```


Expanding the entropy calculation to all coded constructs makes little difference.

```{r}
all_constructs_over_time <- psyctests_info %>% select(subdiscipline_1, DOI, TestYear, Year, ConstructList, usage_count) %>% 
    unnest(ConstructList) %>% 
    rowwise() %>% 
    mutate(construct = unlist(ConstructList)) %>% 
  select(-ConstructList)

entropy_all_constructs <- all_constructs_over_time %>% 
  filter(between(Year, 1993, 2022)) %>% 
  drop_na(construct) %>% 
  group_by(Year, construct) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(n_tests = n_distinct(construct)) %>% 
  group_by(n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(entropy = entropy(n),,
            norm_entropy = calc_norm_entropy(n),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()

byconstruct_entropy_by_year <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  drop_na(first_construct) %>% 
  group_by(Year, Test = first_construct) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(entropy = entropy(n),,
            norm_entropy = calc_norm_entropy(n),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()

entropy_by_year <- bind_rows(# "all tests" = all_entropy_by_year,
                             "all constructs" = entropy_all_constructs,
                             # "by name base" = bybase_entropy_by_year,
                             "first constructs" = byconstruct_entropy_by_year,
                             .id = "version")

entropy_by_year %>% 
  ggplot(., aes(Year, norm_entropy, color = version)) +
  geom_line(size = 0.7) +
  scale_y_continuous("Normalized Shannon Entropy", limits = c(0, 1), labels = scales::percent) +
  # geom_line(aes(y = log(n)), color = 'red') +
  scale_x_continuous("Usage year as coded in APA PsycInfo", limits = c(1993, 2027), 
                     breaks = seq(1993, 2022, by = 1),
                     labels = c(1993, "", "", "", "", 1998, "", "", "", "", 2003, "", "", "", "", 2008, "", "", "", "", 2013, "", "", "", "", 2018, "", "", "", "2022")) +

  scale_color_brewer(type = "qual", guide = "none", palette = 2) +
  # ggrepel::geom_text_repel(
  #   aes(label = str_replace(subdiscipline, " Psychology", "")), data = entropy_by_year %>% filter(Year == max(Year, na.rm = T)),
  #   size = 4, hjust = 1,
  #   ) + 
  geom_text_repel(data = entropy_by_year %>% drop_na() %>% group_by(version) %>% filter(Year == max(Year, na.rm = T)),
                  aes(label = paste0(" ",version)), # "\n (n = ", n_tests, ")"
                  segment.curvature = -0.5,
                  segment.square = TRUE,
                  segment.color = 'grey', 
                  xlim = c(2023, 2030),
                  nudge_x = 1.14,
                  lineheight = .9,
                  hjust = 0,
                  direction="y",
                  na.rm = TRUE) +
  theme_minimal(base_size = 13) +
   theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")


ggsave("figures/entropy_all_vs_first.pdf", width = 8, height = 4)
ggsave("figures/entropy_all_vs_first.png", width = 8, height = 4)
```

## Unbiased estimators of Shannon entropy
Does not make much of a difference.
```{r}
byorig_entropy_by_year <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  mutate(Test = if_else(test_type == "Original", DOI, original_test_DOI)) %>% 
  drop_na(Test) %>% 
  group_by(Year, Test) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(norm_entropy = calc_norm_entropy(n),
            norm_entropy_MM = entropy(n, method = "MM") / log(n()),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()

1 - (byorig_entropy_by_year$n_tests[1]/ records_wide %>% filter(between(TestYear, 1993, 2022)) %>% 
       mutate(Test = if_else(test_type == "Original", DOI, original_test_DOI)) %>% 
       summarise(n_distinct(Test)))


byconstruct_entropy_by_year <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  drop_na(first_construct) %>% 
  group_by(Year, Test = first_construct) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(norm_entropy = calc_norm_entropy(n),
            norm_entropy_MM = entropy(n, method = "MM") / log(n()),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()

all_entropy_by_year <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  drop_na(DOI) %>% 
  group_by(Year, Test = DOI) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(norm_entropy = calc_norm_entropy(n),
            norm_entropy_MM = entropy(n, method = "MM") / log(n()),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()

original_entropy_by_year <- psyctests_info %>% 
  filter(between(Year, 1993, 2022)) %>% 
  filter(test_type == "Original") %>% 
  group_by(Year, Test = DOI) %>% 
  summarise(n = sum(usage_count, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(n_tests = n_distinct(Test)) %>% 
  group_by(n_tests, Year) %>% 
  filter(n > 0) %>% 
  summarise(norm_entropy = calc_norm_entropy(n),
            norm_entropy_MM = entropy(n, method = "MM") / log(n()),
            n = sum(n),
            diff_tests = n()) %>% 
  ungroup()

entropy_by_year <- bind_rows(# "all tests" = all_entropy_by_year,
  "measures" = original_entropy_by_year,
  "with translations\n and revisions" = byorig_entropy_by_year,
  # "by name base" = bybase_entropy_by_year,
  "constructs" = byconstruct_entropy_by_year,
  .id = "version")


plot_entropy <- entropy_by_year %>% 
  ggplot(., aes(Year, norm_entropy, color = version)) +
  geom_line(size = 0.7, linetype = "dashed") +
  geom_line(aes(y = norm_entropy_MM), size = 0.7) +
  scale_y_continuous("Normalized Shannon Entropy", limits = c(0, 1), labels = scales::percent) +
  # geom_line(aes(y = log(n)), color = 'red') +
  scale_x_continuous("Usage year as coded in APA PsycInfo", limits = c(1993, 2027), 
                     breaks = seq(1993, 2022, by = 1),
                     labels = c(1993, "", "", "", "", 1998, "", "", "", "", 2003, "", "", "", "", 2008, "", "", "", "", 2013, "", "", "", "", 2018, "", "", "", "2022")) +
  # ggtitle(str_c(n_distinct(tests_by_year$Test), " measures tracked in PsycInfo")) +
  # annotate("text", x = 1993, y = 1, label = "- each used once", 
  #       size = 3.3, vjust = 0.3, hjust = 0.05) +
  # annotate("text", x = 1993, y = 0, label = "- all used one", 
  #       size = 3.3,  vjust = 0.3, hjust = 0.05) +
  
  scale_color_brewer(type = "qual", guide = "none", palette = 2) +
  # ggrepel::geom_text_repel(
  #   aes(label = str_replace(subdiscipline, " Psychology", "")), data = entropy_by_year %>% filter(Year == max(Year, na.rm = T)),
  #   size = 4, hjust = 1,
  #   ) + 
  geom_text_repel(aes(label = str_replace_all(version, "[a-z=0-9/() ]+", " ")), # This will force the correct position of the link's right end.
                  data = entropy_by_year %>% drop_na() %>% group_by(version) %>% filter(Year == max(Year, na.rm = T)),
                  segment.curvature = -0.1,
                  segment.square = TRUE,
                  lineheight = .9,
                  segment.color = 'grey',
                  box.padding = 0.1,
                  point.padding = 0.6,
                  nudge_x = 1.15,
                  nudge_y = 0.03,
                  force = 0.9,
                  hjust = 0,
                  direction="y",
                  size = 3.3,
                  na.rm = TRUE) +
  geom_text_repel(data = entropy_by_year %>% drop_na() %>% group_by(version) %>% filter(Year == max(Year, na.rm = T)),
                  aes(label = paste0(" ",version)), # "\n (n = ", n_tests, ")"
                  segment.alpha = 0, ## This will 'hide' the link
                  segment.curvature = -0.1,
                  segment.square = TRUE,
                  # segment.color = 'grey',
                  box.padding = 0.1,
                  point.padding = 0.6,
                  nudge_x = 1.15,
                  nudge_y = 0.0,
                  lineheight = .9,
                  force = 0.9,
                  size = 3.3,
                  hjust = 0,
                  direction="y",
                  na.rm = TRUE) +
  theme_minimal(base_size = 13) +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face="bold"),
        legend.position = "none")
plot_entropy
```

## Entropy by classificaiton
```{r}
entropy_by_class <- psyctests_info %>% 
  group_by(classification_1, DOI) %>% 
  summarise(n = sum(usage_count, na.rm = T),
            parent = case_when(
                    n > 50 ~ "",
                    n > 20 ~ "used 21-50 times",
                    n > 5 ~ "used 6-20 times",
                    TRUE ~ "used 1-5 times")) %>% 
  group_by(classification_1) %>% 
  # filter(n > 0) %>% 
  summarise(
    entropy = entropy(n),
    norm_entropy = calc_norm_entropy(n)) %>% 
  arrange(norm_entropy)

kable(entropy_by_class)
```

## Entropy by instrument type
```{r}
psyctests_info %>% 
  group_by(instrument_type_broad, DOI) %>% 
  summarise(n = sum(usage_count, na.rm = T),
            parent = case_when(
                    n > 50 ~ "",
                    n > 20 ~ "used 21-50 times",
                    n > 5 ~ "used 6-20 times",
                    TRUE ~ "used 1-5 times")) %>% 
  group_by(instrument_type_broad) %>% 
  filter(n > 0) %>% 
  summarise(
    entropy = entropy(n),
    norm_entropy = calc_norm_entropy(n)) %>% 
  arrange(norm_entropy) %>% 
  kable()
```

# Tests by exact same name
```{r}
same_name_tests <- records_wide %>% group_by(name_psycinfo) %>% filter(n_distinct(DOI) > 1) %>% summarise(n = n())
nrow(same_name_tests)
mean(same_name_tests$n)
same_name_tests %>% arrange(desc(n)) %>% head(20)
```

